Tourism Data Analysis

### 2019-08-27 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
Repeating the analysis constraining for BoxCox lambda

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)
```

@@

# More analysis on BoxCox transformed resulst

```{r}
DF_BoxCoxTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon, Series) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(R.method == "Base", Forecast_Horizon == 1, 
         F.method %in%c("Bias","Unbiased_M1")) %>% 
  ungroup() %>% 
  dplyr::select(-R.method, -Forecast_Horizon) %>% 
  spread(key = F.method, value = MSE) %>% 
  mutate("Bias-Unbiase" = Bias - Unbiased_M1) %>% 
  filter(`Bias-Unbiase` < -5)

```
Bias correction is giving wiered results for `Total` series.

@@

@@

DF_BoxCoxTrans_Tot_h1 %>% 
  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follow from BoxCox Transformation") + 
  theme(legend.position="bottom")

@@

```{r}
OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]

@@

#generating the hierarchy
#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))

AllTS_new <- allts(Hierarchy) %>%
  as_tibble()

lambda <- numeric()

for (j in 1:140) {#C=140

  Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()

  lambda[j] <- BoxCox.lambda(Train)

}
```

@@

```{r echo=FALSE}
DF_LogTrans %>% 
  filter(Forecast_Horizon == 1) -> DF_LogTrans_h1

DF_LogTrans_h1 %>% 
  filter(Series == "Total", R.method == "Base", F.method == "Bias") %>% 
  dplyr::select(Actual, Replication) -> Total_Log_True

DF_LogTrans_h1 %>% 
  filter(Series == "Total", R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) -> Total_Log_Fc

ggplot() + 
  geom_line(data = Total_Log_Fc, aes(x = Replication, y = Forecasts, color = `F.method`)) + 
  geom_line(data = Total_Log_True, mapping = aes(x = Replication, y = Actual)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follows from Log Transformation")

```{r, echo=FALSE}

>>>>

library(tidyverse)
library(Matrix)
library(hts)
library(readr)
library(tibble)
library(kableExtra)
# library(reshape2)
```

# Box and whisker plots for orthogonal and oblique projections

```{r, echo=FALSE}
OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1]

OvernightTrips_OriginalScale_Fc %>% 
  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2) %>% 
  group_by(`R.method`, Fc_horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE

@@

# More analysis on BoxCox transformed results

```{r echo=FALSE}
DF_BoxCoxTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon, Series) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(R.method == "Base", Forecast_Horizon == 1, 
         F.method %in%c("Bias","Unbiased_M1")) %>% 
  ungroup() %>% 
  dplyr::select(-R.method, -Forecast_Horizon) %>% 
  spread(key = F.method, value = MSE) %>% 
  mutate("Bias-Unbiase" = Bias - Unbiased_M1) %>% 
  filter(`Bias-Unbiase` < -100)

Bias correction is giving wiered results for `Total` series.

@@

# DF_BoxCoxTrans %>% 
#   filter(Forecast_Horizon == 1, Series == "A") -> DF_BoxCoxTrans_A_h1
# 
# DF_BoxCoxTrans %>% 
#   filter(Forecast_Horizon == 1, Series == "B") -> DF_BoxCoxTrans_B_h1

@@

DF_BoxCoxTrans_Tot_h1 %>% 
  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts for Total series follow from BoxCox Transformation") + 
  theme(legend.position="bottom", legend.title = element_blank())

#  DF_BoxCoxTrans_A_h1 %>% 
#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
#   ungroup() %>% 
#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
#   spread(key = F.method, value = Forecasts) %>% 
#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_A_h1
#   
# DF_BoxCoxTrans_A_h1 %>% 
#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
#   ylab("Forecasts/Actual") + 
#   ggtitle("Forecasts for NSW series follow from BoxCox Transformation") + 
#   theme(legend.position="bottom", legend.title = element_blank()) 
#  
#  DF_BoxCoxTrans_B_h1 %>% 
#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
#   ungroup() %>% 
#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
#   spread(key = F.method, value = Forecasts) %>% 
#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_B_h1
#   
# DF_BoxCoxTrans_B_h1 %>% 
#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
#   ylab("Forecasts/Actual") + 
#   ggtitle("Forecasts for Victoria series follow from BoxCox Transformation") + 
#   theme(legend.position="bottom", legend.title = element_blank())

@@

```{r}

DF_BoxCoxTrans_Tot_h1 %>% 
  spread(key = `Forecasts/Actual`, value = Val) %>% 
  mutate("Unb-Act" = Unbiased_M1 - Actual) %>% 
  filter(`Unb-Act`>1000)

Very large bias corrected forecasts are given for some replications. For example in the rolling window Jul-2003 to Oct-2011. Observing the model auto.arima fits:

```{r echo=FALSE}
OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]

@@

#generating the hierarchy
#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
                                                                    3,4,2,3,1,1,1,2,2,3,4))))
AllTS_new <- allts(Hierarchy) %>%
  as_tibble()

L <- 100

```{r echo=FALSE}
j = 67
Train <- AllTS_new[j:(L+j-1),]
TS <- Train[,"Total"] %>% ts(frequency = 12)
fit <- auto.arima(TS, lambda = "auto", biasadj = FALSE, stepwise = FALSE, approximation = FALSE)
Fc <- forecast(fit, h=1)

Fc_trans <- Fc$mean
L_PI <- Fc$lower[,"95%"]
sig_h <- (Fc_trans - L_PI)/1.96
sig2_h <- sig_h^2

summary(fit)

The estimated drift term has a very large standard error. Further the variance of $\hat{y}_{t+1}$ is `r sig2_h` which is very large

@@
